From Reversible Programs to \\ Univalent Universes and Back

### 2017-05-13 upi.tex
question
sec 3 shaping up in content

\begin{tabular}{c@{\qquad\qquad}c}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.7}]]
  \draw (0,-5) ellipse (2cm and 0.8cm);
  \node[below] at (0,-6) {Base Space $\mathbb{1}$};
  \draw[fill] (0,-5) circle [radius=0.025];
  \node[below] at (0,-5) {$\star$};
  \draw (0,-2.7) ellipse (0.5cm and 1cm);
  \node[right] at (0.5,-2.7) {Fiber $P(\star) = \mathbb{2}$};
  \draw[fill] (-0.2,-2.7) circle [radius=0.025];
  \draw[fill] (0.2,-2.7) circle [radius=0.025];
\end{tikzpicture}
&
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.7}]]
  \draw (0,-5) ellipse (2cm and 0.8cm);
  \node[below] at (0,-6) {Base Space $\mathbb{2}$};
  \draw[fill] (-1,-5) circle [radius=0.025];
  \node[below] at (-1,-5) {$\fc$};
  \draw[fill] (1,-5) circle [radius=0.025];
  \node[below] at (1,-5) {$\tc$};
  \draw (0,-2.7) ellipse (0.5cm and 1cm);
  \node[right] at (0.5,-2.7) {Fiber $Q(\fc)$ = Fiber $Q(\tc)$ = $\mathbb{1}$};
  \draw[fill] (0,-2.7) circle [radius=0.025];
  \node[below] at (0,-2.7) {$\star$};
\end{tikzpicture}
\end{tabular}

@@

\bigskip
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.7}]]
  \draw (0,-5) ellipse (2cm and 0.8cm);
  \node[below] at (0,-6) {Base Space $\mathbb{2}$};
  \draw[fill] (-1,-5) circle [radius=0.025];
  \node[below] at (-1,-5) {$\fc$};
  \draw[fill] (1,-5) circle [radius=0.025];
  \node[below] at (1,-5) {$\tc$};
  \draw (-1.3,-2) ellipse (0.5cm and 2cm);
  \node[left] at (-1.8,-2) {Fiber $P(\fc) = \mathbb{0}$};
  \draw (1.3,-2) ellipse (0.5cm and 2cm);
  \node[right] at (1.8,-2) {Fiber $P(\tc) = \mathbb{1}$};
  \draw[fill] (1.8,-2) circle [radius=0.025];
  \draw[below,cyan,dashed,thick] (-1,-5) -- (1,-5);
  \node[below,cyan,dashed,thick] at (0,-5) {$\equiv$};
  \draw[->,red,dashed,ultra thick] (-0.8,-1.7) to [out=45, in=135] (0.8,-1.7);
  \draw[->,red,dashed,ultra thick] (0.8,-2.3) to [out=-135, in=-45] (-0.8,-2.3);
  \node[red,ultra thick] at (0,-2) {$\simeq$};
\end{tikzpicture}

@@

>>>>

\begin{tabular}{c@{\qquad\qquad}c}
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.7}]]
  \draw (0,-5) ellipse (2cm and 0.8cm);
  \node[below] at (0,-6) {Base Space $\mathbb{1}$};
  \draw[fill] (0,-5) circle [radius=0.025];
  \node[below] at (0,-5) {$\star$};
  \draw (0,-2.7) ellipse (0.5cm and 1cm);
  \node[right] at (0.5,-2.7) {Fiber $P(\star) = \mathbb{2}$};
  \draw[fill] (-0.2,-2.7) circle [radius=0.025];
  \draw[fill] (0.2,-2.7) circle [radius=0.025];
\end{tikzpicture}
&
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.7}]]
  \draw (0,-5) ellipse (2cm and 0.8cm);
  \node[below] at (0,-6) {Base Space $\mathbb{2}$};
  \draw[fill] (-1,-5) circle [radius=0.025];
  \node[below] at (-1,-5) {$\fc$};
  \draw[fill] (1,-5) circle [radius=0.025];
  \node[below] at (1,-5) {$\tc$};
  \draw (0,-2.7) ellipse (0.5cm and 1cm);
  \node[right] at (0.5,-2.7) {Fiber $Q(\fc)$ = Fiber $Q(\tc)$ = $\mathbb{1}$};
  \draw[fill] (0,-2.7) circle [radius=0.025];
\end{tikzpicture}
\end{tabular}

@@

\bigskip
\begin{tikzpicture}[scale=0.7,every node/.style={scale=0.7}]]
  \draw (0,-5) ellipse (2cm and 0.8cm);
  \node[below] at (0,-6) {Base Space $\mathbb{2}$};
  \draw[fill] (-1,-5) circle [radius=0.025];
  \node[below] at (-1,-5) {$\fc$};
  \draw[fill] (1,-5) circle [radius=0.025];
  \node[below] at (1,-5) {$\tc$};
  \draw (-1.3,-2) ellipse (0.5cm and 1cm);
  \node[left] at (-1.8,-2) {Fiber $P(\fc) = \mathbb{0}$};
  \draw (1.3,-2) ellipse (0.5cm and 1cm);
  \draw[fill] (1.3,-2) circle [radius=0.025];
  \node[right] at (1.8,-2) {Fiber $P(\tc) = \mathbb{1}$};
  \draw[below,cyan,dashed,thick] (-1,-5) -- (1,-5);
  \node[below,cyan,dashed,thick] at (0,-5) {$\equiv$};
  \draw[->,red,dashed,ultra thick] (-0.8,-1.7) to [out=45, in=135] (0.8,-1.7);
  \draw[->,red,dashed,ultra thick] (0.8,-2.3) to [out=-135, in=-45] (-0.8,-2.3);
  \node[red,ultra thick] at (0,-2) {$\simeq$};
\end{tikzpicture}

@@

%%%
\subsection{A Special Class}

Instead of guessing, there is a special class of univalent fibrations:
\[\begin{array}{rcl}
\{F\} &:& \Sigma_{A:\mathcal{U}} \| F \equiv A \| \rightarrow \mathcal{U} \\
\{F\}(A,|p|) &=& A
\end{array}\]

This construction is always a univalent fibration~\cite{XXX}. We can understand
the basic idea as follows. Take two points $(A,|p|)$ and $(B,|q|)$ in the base
space. We want to compare the space $A \simeq B$ with the space
$(A,|p|) \equiv (B,|q|)$.  In one direction, we have $p : F \equiv A$ and
$q : F \equiv B$ and hence $A \equiv B$ and by univalence $A \simeq B$. In the
other direction \ldots

Also explain base space has higher paths \ldots
